Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Remove redundant "implementation".
Fix typo: make plural noun so.

The implementation of the Raft algorithm is implemented in the
\texttt{RaftServerBase} class (in \texttt{base.js}). The base class
omits the implementation of functions with side-effect such as RPC
communication, durable storage, scheduling/timeouts, or state machine
command/management. In order to create a working implementation these
functions must be provided either as configuration parameters when the
class is instantiated or by sub-classing the class.

>>>>

The implementation of the Raft algorithm is in the
\texttt{RaftServerBase} class (in \texttt{base.js}). The base class
omits the implementation of functions with side-effects such as RPC
communication, durable storage, scheduling/timeouts, or state machine
command/management. In order to create a working implementation these
functions must be provided either as configuration parameters when the
class is instantiated or by sub-classing the class.
